% Remerciements
%
%   Grâce aux remerciements, l'auteur attire l'attention du lecteur
% sur l'aide que certaines personnes lui ont apportée, sur leurs
% conseils ou sur toute autre forme de contribution lors de la
% réalisation de son mémoire. Le cas échéant, c'est dans cette section
% que le candidat doit témoigner sa reconnaissance à son directeur de
% recherche, aux organismes dispensateurs de subventions ou aux
% entreprises qui lui ont accordé des bourses ou des fonds de
% recherche.
\chapter*{ACKNOWLEDGEMENTS}\thispagestyle{headings}
\addcontentsline{toc}{compteur}{ACKNOWLEDGEMENTS}
%

I would like to thank my research director, Giuliano Antoniol of the Software Engineering Department at Ecole Polytechnique de Montreal. You were always there when I needed support and made yourself available for me. You shared with me your experience and knowledge as well as an ear in times of need. You manifested a lot of comprehension and patience, particularly considering my peculiar study background. I would also like to thank you for giving me the chance to pursue my studies in a domain so different from my previous ones, and for trusting me from the first to the last day. \\

I would also like to express my profound gratitude to my parents for always supporting me emotionally and financially during all those years of studying. It has been a long run since I started attending school, but your support and encouragement definitely made a huge positive difference in my success. Without you, I would not be where and who I am today. Thank you. \\

C\'{e}dric Noiseux